\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

%\pagestyle{fancy}
\fancyhf{}
\lhead{}
\chead{}
\rhead{}
\rfoot{\thepage/ \pageref{LastPage}}
\lfoot{Jason Bane}
\cfoot{jbane@jlab.org}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
		{\setlength{\leftmargin}{#1}}%
		\item[]%
	}
	{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
		{\setlength{\leftmargin}{-0.5#1}}%
		\item[]%
	}
	{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
		#1 &
		#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\vspace*{-1.2cm}
\noindent Jason Bane\\
18 Morrison Ave. \\
Newport News, VA 23601 \\
jbane@jlab.org \\
\today\\

\noindent Dr. Peng,\\
Canon Medical Systems Corporation\\
Vernon Hills, IL\\




Dear Dr. Peng, 

\paragraph{}I write to apply for the post doctoral fellow position working on PET instrumentation. I successfully defended my dissertation "The EMC Effect in A=3 Nuclei" under the direction of Nadia Fomin, at the University of Tennessee. My dissertation research brought me to Thomas Jefferson National Laboratory in Newport News, VA. My time at the lab has been devoted to honing my skills and knowledge in the complete process of being an experimental physicist. I experienced constructing spectrometers, refurbishing detectors, building electrical systems for data acquisition, analyzing large data sets, and collaborating with a diverse community while working with three electron scattering experimental groups.
\paragraph{}My research at Jefferson Lab has allowed me to work on many aspects of an experiment. I collaborated with a diverse group of scientists to construct, maintain, and operate three electron spectrometers to extract the electron-nucleus inclusive cross section. I aspire to continue developing and growing my skills in radiation detection and data analysis. This includes improving my understanding of hardware and software used in my previous research but also translating my current experiences to be useful with the tools and methods of other research arenas. My career aspirations are centered around education. Educating myself first, gaining new experiences, learning new tools, and developing new skills. Then I want to help facilitate the dissemination of this knowledge through a career in education, mentoring colleagues, or communicated to a collaboration.  Joining the Canon team would allow me to fulfill my research interest and career goals by connecting my current hardware and software experiences to the medical physics arena and continuing to develop my knowledge.


\iffalse
\paragraph{}My time at Jefferson Lab has allowed me to work on many aspects of an experiment. I was able to work on the refurbishment and maintenance of a large acceptance electron spectrometer for a tritium experiment. Preparing this spectrometer gave me the opportunity to gain experience in the design and construction of the front end electronics. I refurbished individual detectors, by testing and replacing photomultiplier tubes and scintillating plastics. I assembled and tested the data acquisition system.
I also prepared part of the analysis software and completed analysis for three different experiments by helping maintain the online analysis software and data decoding scripts. I calibrated parts of the detectors, focusing on the beam position monitors and analog to digital converter signals from the Cherenkov and calorimeters. As part of my Ph.D., I have been analyzing electron scattering data to extract complete cross sections. I have worked closely with cross-section models and Monte Carlo simulation packages. Completing this analysis has granted me the ability to learn different coding languages like \CPP, Fortran, ROOT, and python. Being a senior student at the lab has allow me to take on roles as a mentor and guide for many of the new students, instructing them on the use of the detectors and analysis software.
\fi
\paragraph{}The knowledge and skills I have gained working at Jefferson Lab would make me a great fit to work with the Canon community. My mixture of hardware, software and teaching experiences will allow me to quickly step into the roles needed, including collaborating with a team, working with the detector designs and development, and analyzing data to characterize the PET scanners.      
\\

Currently, I finishing graduation requirements to receive my diploma in December and I am able to start working on December 23rd. I submitted a CV that contains the contact information for three references along with this letter in the application and in email. 
\\

\noindent Thank you for your time and attention,\\
\noindent Jason Bane




\end{document}

