
\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fancyhdr}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\pagestyle{fancy}
\fancyhf{}
\lhead{}
\chead{}
\rhead{}
\rfoot{\thepage}
\lfoot{Jason Bane}
\cfoot{jbane@jlab.org}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Jason Bane}}

18 Morrison Ave.\ \ \textbullet
\ \ Newport News, VA 23601 \\
(931) 239-0611\ \ \textbullet
\ \ jbane@jlab.org
\end{center}
\hrule


\subsection*{References}
\begin{multicols}{2}
	{\bf{Nadia Fomin}}, Professor\\
	Department of Physics and Astronomy\\ 
	University of Tennessee at Knoxville\\
	(865) 974-1509, fomin@vols.utk.edu\\
	\columnbreak
	
	{\bf{Douglas Higinbotham}}, Staff Scientist\\
	Jefferson Lab Accelerator Facility\\
	(757) 584-7851, doug@jlab.edu\\
\end{multicols}

\begin{multicols}{2}
	{\bf{Evan McClellan}}, Post-doctoral Fellow\\
Jefferson Lab Accelerator Facility\\
randallm@jlab.org\\

	\columnbreak
		{\bf{Mellisa White}}, Teacher, Principal\\
	Clay Count Board of Education\\
	millicentfiske@gmail.com\\

\end{multicols}

\subsection*{Publications}
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item  H. Dai, [et al. including \textbf{J. Bane}], ``First Measurement of the Ar(e,$e^\prime$)X Cross Section at Jefferson Lab," Phys. Rev. C 99, 054608 May 2019
	\item R. Cruz-Torres, [et al. including \textbf{J. Bane}], ``Comparing proton momentum distributions in A=3 nuclei via $^3$He and $^3H$(e,$e^\prime$p) measurements," in preparation, (2019)
	\item S. N. Santiesteban, S. Alsalmi, D. Meekins, \textbf{J. Bane,} et al., ``Density Changes in Low Pressure Gas Targets for Electron Scattering Experiments" in preparation (2018) 
	
	\item  H. Dai, [et al. including \textbf{J. Bane}], ``First Measurement of the Ti(e,$e^\prime$)X Cross Section at Jefferson Lab," Phys. Rev. C 98, 014617 July 2018
	\item P V. Pandey, [et al. including \textbf{J. Bane}], ``Probing electron-argon scattering for liquid-argon based neutrino-oscillation program," preprint arXiv:1711.01671
	
\end{itemize}
\hrule

\subsection*{Conference Presentations}
\begin{itemize*}
	\item "EMC in A=3 from MARATHON," 2nd Workshop on Quantitative Challenges in SRC and EMC Research,  MIT, Cambridge MA,  March 2019
	\item "Ratios in A=3 nuclei from MARATHON ," American Physical Society's Division of Nuclear Physics' yearly meeting, HA, October 2018
	\item "Measurement of the spectral function of Argon and Titanium through the(e,$e^\prime$p) reaction," American Physical Society's Division of Nuclear Physics' yearly meeting, HA, October 2018
	\item "Status of the MARATHON experiment." American Physical Society's Division of Nuclear Physics' yearly meeting, Pittsburgh PA, October 2017
	\item "Searching for the Origin of the EMC effect." American Physical Society's Division of Nuclear Physics' yearly meeting, Sante Fe NM, October 2016
\end{itemize*}

\hrule
\subsection*{Poster Presentations}
\begin{itemize*}
	\item "The impetus in the EMC effect, a EMC simulation." Gordon Research Conferences, Holderness, NH. August 2018 
	\item "Searching for the Origin of the EMC effect." SURA Board of Trustees Meeting, Newport News, VA. April 2018 
\end{itemize*}


\end{document}
